Tropical mathematics and the Lambda-calculus I

### 2023-08-02 CSL24/sectionTaylip.tex
commit

\begin{corollary}
Suppose $x: A \vdash_{\STLC}M:B$ and $\vdash_{\STLC} N:A$. 
Then for all $t\in \Te{M}$ such that $\model{t}^{!}(\model{N})\neq \infty$, and $\delta>0$, the tps $\model{ x:A\vdash_{\STLC}M:B}^{!}$ is $\frac{\model{t}^{!}(\model{N}+2\delta)}{\delta}$-Lipschitz over the open ball
 $B_{\delta}(\model{N})$.
\end{corollary}
\begin{proof}
We apply the Lipschitz estimate from Thm.~\ref{thmTLSlocLip} for $\model{M}^{!}$,  and use the fact that, from Thm.~\ref{thm:taylor} 4.~it follows that $\model{t}^{!}\geq \model{M}^{!}$.
To conclude, since $\model{t}^{!}$ is concave and non-decreasing, $\max_{\overline{B_{3\delta}(x)}}\model{t}^{!}= \model{t}^{!}(x+3\delta)$, which yields the stated Lipschitz estimate. 
\end{proof}
%{\color{red}ADD PROOF SKETCH}

>>>>

\begin{corollary}\label{cor:taylor}
Suppose $x: A \vdash_{\STLC}M:B$ and $\vdash_{\STLC} N:A$. 
Then for all $t\in \Te{M}$ such that $\model{t}^{!}(\model{N})\neq \infty$, and $\delta>0$, the tps $\model{ x:A\vdash_{\STLC}M:B}^{!}$ is $\frac{\model{t}^{!}(\model{N}+2\delta)}{\delta}$-Lipschitz over the open ball
 $B_{\delta}(\model{N})$.
\end{corollary}
\begin{proof}[Proof sketch.]
We apply the Lipschitz estimate from Thm.~\ref{thmTLSlocLip} for $\model{M}^{!}$,  and use the fact that, from Thm.~\ref{thm:taylor} 4.~it follows that $\model{t}^{!}\geq \model{M}^{!}$.
To conclude, since $\model{t}^{!}$ is concave and non-decreasing, $\max_{\overline{B_{3\delta}(x)}}\model{t}^{!}= \model{t}^{!}(x+3\delta)$, which yields the stated Lipschitz estimate. 
\end{proof}
%{\color{red}ADD PROOF SKETCH}
